%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {Stealth mode startup} % Organization
  {Hyderabad, India(Remote)} % Location
  {Oct. 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Building an e-commerce product ranking system using conjoint analysis.}
    \end{cvitems}
  }
  \cventry
    {Senior Software Engineer} % Job title
    {Turing Inc} % Organization
    {Hyderabad, India(Remote)} % Location
    {Apr. 2020 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supply Chain Product}
        \begin {itemize}
          \item Developed a supply chain product to streamline inventory procurement and management for the client's manufacturing plants.
          \item Implemented a robust system using Python to enhance the supply chain operations.
          \item Leveraged AWS services for scalable and reliable infrastructure.
          \item Designed and implemented a GraphQL-based interface for efficient data querying and manipulation.
          \item Utilized DynamoDB for secure and efficient data storage.
          \end{itemize}
        The project was a resounding success, contributing to the optimization of the client's manufacturing operations.
	\item {CRM}
      \begin {itemize}
        \item Developed a CRM product for lawyer data management in the USA and Canada.
        \item Created REST and GraphQL APIs using Python and Django, facilitating integration with multiple platforms.
        \item Utilized PostgreSQL and Redis for efficient data storage.
        \item Implemented a microservices architecture to gather and analyze data from various sources, including phone and email services.
        \item Developed the core functionalities of the CRM using Python.
        \item Utilized the Django framework to build the web application and APIs.
        \item Designed and deployed microservices to collect and analyze data.
      \end{itemize}
        Successfully deployed and adopted by thousands of lawyers in the USA and Canada.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {Setuserv Info. Pvt. Ltd.} % Organization
    {Hyderabad, India} % Location
    {Aug. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Text Analytics System}
        \begin {itemize}
          \item Designed a service architecture for an NLP-based text analytics SaaS product using a microservices approach.
          \item Established an end-to-end pipeline infrastructure on AWS, incorporating multi-node Kafka, Cassandra/Scylla, a web crawler, and other critical services.
          \item Developed a RESTful API to enable end-users to access data, while internal micro-services communicated through gRPC API.
          \item Created a user-friendly web portal for visualizing analytics, offering thousands of filters to generate millions of possible combinations.
          \item Led and managed a team of six engineers throughout the project.
          \end{itemize}
        Successfully delivered the project, providing a powerful text analytics solution with a user-friendly interface and robust infrastructure.
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO/Technical Architect} % Job title
    {Ebizon Net Info Pvt. Ltd.} % Organization
    {Noida, India} % Location
    {Jul. 2015 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{PushFlew (\href{https://pushflew.com}{https://pushflew.com})}
        \begin{itemize}
        \item Developed PushFlew (https://pushflew.com), a SaaS product tailored for small and medium-sized enterprises, focusing on customer life-cycle management.
        \item Provided push and email notification services for web applications.
        \item Implemented public-private key pairs for each registered website, with the public key stored client-side using a JavaScript plugin for service worker registration.
        \item Utilized a private key on the backend for secure push notification payload signing.
        \item Incorporated features such as automated pushes from RSS feeds and e-commerce-specific activities like cart abandonment and shipping notifications.
        \item Employed Scala for various backend functionalities.
        \item Utilized PostgreSQL and Redis for efficient data storage.
        \item Ensured consistent deployment through containerization.
        \item Designed RESTful APIs for seamless integration.
        \item Developed a JavaScript plugin for client-side integration.
      \end{itemize}
        Successfully delivered PushFlew, a versatile customer life-cycle management solution for web applications.
        \item{AppifyCart (\href{https://appifycart.com}{https://appifycart.com})}
        \begin{itemize}
          \item Created AppifyCart (https://appifycart.com), a SaaS product designed for e-commerce companies to build and manage mobile apps for iOS and Android.
          \item Streamlined the process of app creation by allowing users to upload basic details and API keys for their e-commerce store.
          \item Empowered users to manage app features, including payment gateways and shipping methods, after app deployment to app stores.
          \item Utilized Scala for critical backend components.
          \item Managed data using PostgreSQL and MongoDB for specific data requirements.
          \item Supported both iOS and Android app development.
          \item Designed RESTful APIs for seamless integration with e-commerce platforms.
          \end{itemize}
        Successfully delivered AppifyCart, a user-friendly SaaS solution for building and managing mobile apps for e-commerce companies.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Specialist} % Job title
    {Geometric Ltd.} % Organization
    {Pune, India} % Location
    {Apr. 2010 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Simulation of virtual cloths}
        \begin{itemize}
        \item Led a team of five engineers in the development of a cloth simulation engine.
        \item Implemented advanced physics and geometry algorithms for realistic virtual cloth simulation.
        \item Leveraged GPU computing for efficient and high-performance cloth simulations.
        \item Integrated the simulation APIs with a user-friendly interface using WPF (Windows Presentation Foundation) and OpenGL.
        \item Established a shared memory system to facilitate seamless data transfer between the CPU, GPU, and visualization components.
        \item Utilized C++ for the core development of the cloth simulation engine.
        \end{itemize}
        Successfully delivered a cloth simulation engine that is in active use by clients, enabling realistic virtual cloth simulations for various applications.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CSC India Pvt. Ltd.(PayPal IDC)} % Organization
    {Chennai, India} % Location
    {Oct. 2007 - Mar. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Automated risk mitigation payments}
        \begin{itemize}
          \item Developed risk mitigation products for PayPal Payments.
          \item Implemented a rules-engine for Payment stream and batch processing.
          \item Created an address normalization product to verify addresses and reduce risk.
          \item Designed batch processing tools to analyze payment and risk data.
          \item Presented the analyzed data through a visual dashboard.
          \item Utilized C++ and Python for software development.
          \item Employed Oracle for data management and storage.
        \end{itemize}
        The product is actively used in processing millions of USD daily, effectively mitigating risk in PayPal Payments.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Geometric Ltd.} % Organization
    {Pune, India} % Location
    {Jan. 2005 - Sep. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{PreClassA Library}
        \begin{itemize}
          \item Developed PreClassA Library for automated Class A Surface creation.
          \item Implemented an optimization module using Quadratic Programming.
          \item Designed a feature for merging multiple Class A surfaces with g2 continuity.
          \item Developed and applied a solution to fill missing STL cloud data points for Class A surfaces.
          \item Utilized C++ for software development, enabling efficient surface creation and optimization.
        \end{itemize}
        The product is widely used in modern automobile design, streamlining the process of creating Class A surfaces for automotive products.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Research Fellow} % Job title
    {IIT Bombay} % Organization
    {Mumbai, India} % Location
    {Aug. 2004 - Jan. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimization in CAGD}
        \begin{itemize}
          \item Conducted research in Computer-Aided Geometric Design (CAGD).
          \item Achieved successful automation of Class A surface creation.
          \item Proficient in MATLAB for research and software implementation.
          \end{itemize}
        Implemented the research findings into software solutions benefiting the automotive industry.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
